---
title: "Case Study"
output: html_document
date: "2025-10-07"
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(readxl)
library(haven)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r}
library(p8105.datasets)

data(nyc_airbnb)
```


## Brainstorm questions
* Pick a neighborhood / borough, investigate price
  * If we had dates, does that affect price?
* Does the type of unit affect rating / price?
* What about ZIP codes?
* What rental has the highest reviews?
* Are there any connections between price and other variables?
* What about prices over time?
  * Could we look at prices before and after the pandmeic?
* How else did the pandemic affect Air BNB in NYC?
* Does the name of the rental affect the price / rating?
* What does the number of days available have to do with anything else?

```{r}

```

## How does borough affect average price?
```{r}
nyc_airbnb |>
  mutate(avg_price = mean(price)) |>
  group_by(neighbourhood_group) |>
  summarise(avg_price = mean(price, na.rm = TRUE))
```
Manhattan has the greatest average price of $180, followed by SI, Brooklyn, Queens, and the Bronx.

## Focus in on Manhattan
```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 500,
         room_type == "Entire home/apt") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))
```

(remember to look at extreme values ...)
```{r}
nyc_airbnb |>
  filter(price>9000) |>
  view()
```

```{r}
nyc_airbnb |>
  filter(calculated_host_listings_count > 30)
```


## What about room type in a given neighborhood?
```{r}
nyc_airbnb |>
  drop_na(price) |>
  group_by(room_type, neighbourhood_group) |>
  summarize(
    avg_price = mean(price)
  ) |>
  pivot_wider(
    names_from=room_type, 
    values_from=avg_price
  )
```


```{r}
nyc_airbnb |>
  count(neighbourhood_group, room_type)

```

Make some plots
```{r}
nyc_airbnb |>
  ggplot(aes(x=price)) +
  geom_histogram() +
  facet_grid(room_type ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 1000)) 
```


## Leaflet
```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location
)

nyc_airbnb |>
  filter(
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt") |>
  leaflet() |>
  addProviderTiles(providers$CartoDB.Positron) |>
  addCircleMarkers(~lat, ~long, 
                   color = ~pal(review_scores_location), radius=2) 
```
Need to render this to an HTML document!
